Something that is not PCADSC

### 2017-02-19 article/article_v0.01.tex
Minor language stuff

\section{Introduction}
\label{sec:introduction}
The origin stories of datasets have changed over time. While data, in the past, data was collected with a specific scientific inquiry in mind, today, a lot of data is accumulated without a specific purpose. This is due to vast amounts of data being registered online and due to a trend towards more open source research. The latter phenomenon, in particular poses new challenges wrt.\ data quality assessment. When data are collected and made public without a specific end-point in mind, how do we ensure that e.g.\ differences in measurement instruments do not cause the data to be effectively divided into subsets that are simply not comparable?

>>>>

\section{Introduction}
\label{sec:introduction}
The origin stories of datasets have changed over time. While in the past, data was often collected with a specific scientific inquiry in mind, today, a lot of data is accumulated without such a specific purpose. This is due to vast amounts of data being registered online and due to a trend towards more open source research. The latter phenomenon in particular poses new challenges wrt. data quality assessment. When data are collected and made public without a specific end-point in mind, how do we ensure that e.g.\ differences in measurement instruments do not cause the data to be effectively divided into subsets that are simply not comparable?
